Modal Abstractions for Virtualizing Memory Addresses

### 2024-07-10 examples.tex
+

   \forall_{\textsf{i}\in\textsf{0..511}} \ldotp \paddr + \textsf{i * 8} \mapsto_{\textsf{id,qfacc}} \textsf{mvalidc} \ast \ulcorner \textsf{qfrac} = 1 \leftrightarrow \; \lnot\textsf{entry\_present }(\vale) \urcorner \ast \\

>>>>

   \forall_{\textsf{i}\in\textsf{0..511}} \ldotp \paddr + \textsf{i * 8} \mapsto_{\textsf{id,qfacc}} \textsf{mvalidc} \ast  \underbrace{ \ulcorner \textsf{qfrac} = 1 \leftrightarrow \; \lnot\textsf{entry\_present }(\vale) \urcorner}_\text{Entry validity}\ast \\
